Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-27 fmics/paper.tex
Revise intro paragraph about inductive reasoning

In this paper, we describe a formal verification approach based on logical deduction for analyzing the SRS implementation.
Our high level proof strategy takes advantage of the regular structure of the SRS.
This structure consists of multiple layers of shift registers and some simple arithmetic hardware.
There is a degree of regularity in how the output of each layer is used as input to the next layer of this structure.
There is also a degree of regularity in the timing of each layer with respect to its position in the stack of layers.
This regularity serves as the basis of using inductive reasoning, which allows us to keep the amount of verification effort linear with respect to the number of layers in the SRS structure even though the ``state space" of the possible values of the structure increases exponentially with the number of layers.
{\bf Ramana, please verify if this is actually true, that is, we use induction}

>>>>

In this paper, we describe a formal verification approach based on logical deduction for analyzing the SRS implementation.
Our high level proof strategy takes advantage of the regular structure of the SRS, which consists of multiple layers of shift registers and some simple arithmetic hardware.
There is a degree of regularity in how the output of each layer is used as input to the next layer.
There is also a degree of regularity in the timing of each layer with respect to its position in the stack of layers.
This regularity serves as a basis for inductive reasoning, which makes the amount of verification effort impervious to the number of layers in the structure.
